---
title: "Co-diffusion"
author: "CYP"
date: "2020/5/3"
output: word_document
---


# US one way

## Cases 2020/03/07 - 2020-04-24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
M       | 1.3159331  | 0.0640758   | 20.537   | < 2e-16    | ***
P       | 0.0016618  | 0.0002744   | 6.057    | 2.38e-07   | ***
Q       | 0.1095144  | 0.0072015   | 15.207   | < 2e-16    | ***

##  News 2020/01/11 - 2020-04-24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P | 0.003478  | 0.000480  | 7.247 | 8.40e-11 | ***
Q | 0.033066  | 0.002797  | 11.824 |  < 2e-16 | ***
c1 | 0.045329  | 0.008164 |  5.552 | 2.25e-07 |  ***
```{r}
# one-way effect
# cases add on news

# from 2020-03-07 to 2020-04-24
Cases <- c(139, 120, 68, 354, 322, 382, 516, 547, 773, 1133, 1789, 1365, 5894, 5421, 6413, 8334, 9815, 10073, 12042, 18058, 17821, 19808, 19444, 20922, 26341, 25200, 30227, 31987, 33267, 28219, 29595, 29556, 32829, 32385, 35098, 29861, 28917, 25306, 27051, 28680, 31451, 31905, 32491, 26889, 25240, 27539, 28355, 28950, 36163)

# from 2020-01-11 to 2020-04-24
News <- c(13, 14, 21, 24, 35, 33, 25, 9, 14, 38, 31, 33, 33, 44, 19, 18, 36, 33, 37, 35, 37, 14, 17, 25, 26, 25, 41, 31, 24, 16, 22, 30, 24, 32, 27, 13, 17, 29, 19, 36, 27, 32, 15, 17, 27, 33, 43, 35, 46, 26, 17, 44, 50, 43, 40, 52, 21, 21, 49, 46, 47, 56, 45, 29, 36, 69, 66, 60, 62, 66, 24, 27, 48, 69, 48, 60, 67, 31, 36, 58, 75, 65, 49, 41, 41, 36, 47, 74, 57, 72, 53, 44, 26, 54, 64, 49, 49, 65, 22, 25, 58, 51, 53, 57, 51)

Cases <- Cases/sum(Cases)
T_day <- 1:length(Cases)
c_nls <- nls(
  Cases ~ M * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day)) / (1 + (Q / P) * exp(-(P + Q) * T_day)) ^ 2,
  start=list(M=1, P=0.003, Q=0.038)
  #start=list(M=10000, P=0.003, Q=0.38)
)
summary(c_nls)

cases_coef <- coef(c_nls)
m_c <- cases_coef[1]
p_c <- cases_coef[2]
q_c <- cases_coef[3]

News <- News / sum(News)
T_day_news <- 1:length(News)
zeroes = length(T_day_news) - length(T_day)
T_day <- c(rep(0, zeroes), T_day)
# estimates of news come in to the formula to perform co-diffusion
# c1 is coefficient of cases
# F = (1 - exp(-(P + Q) * t)) / (1 + (Q / P) * exp(-(P + Q) * t))
# News ~ M * f1 = M * (原本bass那串 + c1 * F2(t) * (1 - F1(t)))
n_nls <- nls(
  News ~ 1 * ((((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2 + c1 * (1 - exp(-(p_c + q_c) * T_day)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * T_day)) * (1 - (1 - exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)))),
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.03, Q=0.038, c1=0.1)
  #start=list(M=3, P=0.03, Q=0.0038, c1=0.1),
)
summary(n_nls)

news_coef <- coef(n_nls)
p_n <- news_coef[1]
q_n <- news_coef[2]
c1_n <- news_coef[3]
m_n <- 1





# w/o co-diffusion
n_wo_cd_nls <- nls(
  News ~ 1 * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2,
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.03, Q=0.038)
  #start=list(M=3, P=0.03, Q=0.0038, c1=0.1),
)
summary(n_wo_cd_nls)
news_wo_cd_coef <- coef(n_wo_cd_nls)
p_n_wo_cd <- news_wo_cd_coef[1]
q_n_wo_cd <- news_wo_cd_coef[2]
m_n_wo_cd <- 1






# simulation
Tdelt <- (1:(length(Cases) * 10)) / 10
ngete <- exp(-(p_c + q_c) * Tdelt)
cpdf <- m_c * ((p_c + q_c) ^ 2 / p_c) * ngete / (1 + (q_c / p_c) * ngete) ^ 2

Tdelt <- (1:(length(News) * 10)) / 10
Tdelt_cases <-ifelse(Tdelt - zeroes < 0, 0, Tdelt - zeroes)
ngete <- exp(-(p_n + q_n) * Tdelt)
npdf <- m_n * (((p_n + q_n) ^ 2 / p_n) * ngete / (1 + (q_n / p_n) * ngete) ^ 2 + c1_n * (1 - exp(-(p_c + q_c) * Tdelt_cases)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * Tdelt_cases)) * (1 - (1 - exp(-(p_n + q_n) * Tdelt)) / (1 + (q_n / p_n) * exp(-(p_n + q_n) * Tdelt))))

cpdf <- c(rep(0, zeroes * 10), cpdf)
Cases <- c(rep(0, zeroes), Cases)

ngete_wo_cd <- exp(-(p_n_wo_cd + q_n_wo_cd) * Tdelt)
n_wo_cd_pdf <- m_n_wo_cd * ((p_n_wo_cd + q_n_wo_cd) ^ 2 / p_n_wo_cd) * ngete_wo_cd / (1 + (q_n_wo_cd / p_n_wo_cd) * ngete_wo_cd) ^ 2

# cases is higher so plot cases first
plot(cpdf ~ Tdelt, col=5, type='l', xlab = "Day from 1/11", ylab = "Quantity", main = "Co-diffusion of cases and news in US")
points(T_day_news, Cases, col=5, pch=6)
points(News ~ T_day_news, col='blue', pch=4)
lines(Tdelt, npdf, col='blue')
lines(Tdelt, n_wo_cd_pdf, col='red', lty=2)
legend("topleft",
       pch = c(6, 4),
       col = c(5, 'blue'),
       legend = c("Cases", "News")
       )
```

# UK one way

## Cases 2020/03/12 - 2020/04/24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
M| 1.3123825|  0.0830045|   15.81|  < 2e-16| ***
P| 0.0024500 | 0.0004571 |   5.36 |3.74e-06 |***
Q| 0.1149791  |0.0100024  | 11.49 |2.99e-14 |***

##  News 2020/01/11 - 2020-04-24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P|  0.002368|   0.000303|   7.814| 5.15e-12| ***
Q | 0.040532 |  0.002311 | 17.539 | < 2e-16 |***
c1 |0.058339  | 0.008946  | 6.521 |2.72e-09 |***
```{r}
# one-way effect
# cases add on news

# from 2020-03-12 to 2020-04-24
# cases data is not cleaned
Cases <- c(342, 342, 140, 407, 409, 682, 74, 1298, 1053, 674, 985, 1438, 1476, 2172, 2933, 2567, 2468, 2673, 3028, 4384, 4308, 4516, 3788, 5959, 3843, 3670, 5525, 4398, 8733, 5269, 5332, 4364, 5275, 4638, 4662, 5624, 5545, 5858, 4684, 4316, 4466, 4608, 5394)

# from 2020-01-11 to 2020-04-24
News <- c(9, 9, 21, 26, 20, 26, 25, 18, 10, 28, 18, 18, 45, 41, 21, 31, 30, 38, 38, 39, 22, 11, 11, 14, 16, 11, 8, 19, 35, 32, 59, 61, 53, 59, 61, 31, 40, 75, 44, 53, 59, 53, 44, 73, 80, 81, 69, 51, 105, 67, 49, 110, 74, 79, 76, 87, 40, 47, 95, 81, 68, 72, 71, 70, 50, 92, 68, 77, 71, 57, 55, 57, 69, 90, 86, 96, 100, 66, 67, 81, 94, 84, 119, 12, 135, 142, 89, 93, 111, 91, 98, 67, 76, 88, 92, 98, 114, 97, 64, 97, 87, 97, 98, 88, 107)

Cases <- Cases / sum(Cases)
T_day <- 1:length(Cases)
c_nls <- nls(
  Cases ~ M * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day)) / (1 + (Q / P) * exp(-(P + Q) * T_day)) ^ 2,
  start=list(M=4, P=0.001, Q=0.1)
  #start=list(M=10000, P=0.003, Q=0.38)
)
summary(c_nls)

cases_coef <- coef(c_nls)
m_c <- cases_coef[1]
p_c <- cases_coef[2]
q_c <- cases_coef[3]

News <- News / sum(News)
T_day_news <- 1:length(News)
zeroes = length(T_day_news) - length(T_day)
T_day <- c(rep(0, zeroes), T_day)
# estimates of news come in to the formula to perform co-diffusion
# c1 is coefficient of cases
# F = (1 - exp(-(P + Q) * t)) / (1 + (Q / P) * exp(-(P + Q) * t))
# News ~ M * f1 = M * (原本bass那串 + c1 * F2(t) * (1 - F1(t)))
n_nls <- nls(
  News ~ 1 * ((((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2 + c1 * (1 - exp(-(p_c + q_c) * T_day)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * T_day)) * (1 - (1 - exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)))),
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.03, Q=0.038, c1=0.1)
)
summary(n_nls)

news_coef <- coef(n_nls)
p_n <- news_coef[1]
q_n <- news_coef[2]
c1_n <- news_coef[3]
m_n <- 1



# w/o co-diffusion
n_wo_cd_nls <- nls(
  News ~ 1 * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2,
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.003, Q=0.038)
  #start=list(M=3, P=0.03, Q=0.0038, c1=0.1),
)
summary(n_wo_cd_nls)
news_wo_cd_coef <- coef(n_wo_cd_nls)
p_n_wo_cd <- news_wo_cd_coef[1]
q_n_wo_cd <- news_wo_cd_coef[2]
m_n_wo_cd <- 1



# simulation
Tdelt <- (1:(length(Cases) * 10)) / 10
ngete <- exp(-(p_c + q_c) * Tdelt)
cpdf <- m_c * ((p_c + q_c) ^ 2 / p_c) * ngete / (1 + (q_c / p_c) * ngete) ^ 2

Tdelt <- (1:(length(News) * 10)) / 10
Tdelt_cases <-ifelse(Tdelt - zeroes < 0, 0, Tdelt - zeroes)

ngete <- exp(-(p_n + q_n) * Tdelt)
npdf <- m_n * (((p_n + q_n) ^ 2 / p_n) * ngete / (1 + (q_n / p_n) * ngete) ^ 2 + c1_n * (1 - exp(-(p_c + q_c) * Tdelt_cases)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * Tdelt_cases)) * (1 - (1 - exp(-(p_n + q_n) * Tdelt)) / (1 + (q_n / p_n) * exp(-(p_n + q_n) * Tdelt))))

cpdf <- c(rep(0, zeroes * 10), cpdf)
Cases <- c(rep(0, zeroes), Cases)


ngete_wo_cd <- exp(-(p_n_wo_cd + q_n_wo_cd) * Tdelt)
n_wo_cd_pdf <- m_n_wo_cd * ((p_n_wo_cd + q_n_wo_cd) ^ 2 / p_n_wo_cd) * ngete_wo_cd / (1 + (q_n_wo_cd / p_n_wo_cd) * ngete_wo_cd) ^ 2



# cases is higher so plot cases first
plot(cpdf ~ Tdelt, col=5, type='l', xlab = "Day from 1/11", ylab = "Quantity", main = "Co-diffusion of cases and news in UK")
points(T_day_news, Cases, col=5, pch=6)
points(News ~ T_day_news, col='blue', pch=4)
lines(Tdelt, npdf, col='blue')
lines(Tdelt, n_wo_cd_pdf, col='red', lty=2)
legend("topleft",
       pch = c(6, 4),
       col = c(5, 'blue'),
       legend = c("Cases", "News")
       )
```

# AU one way

## Cases 2020/03/13 - 2020/04/24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P| 0.006141 |  0.001029|    5.97| 4.78e-07| ***
Q |0.227823  | 0.013657 |  16.68 | < 2e-16 |***

##  News 2020/01/11 - 2020-04-24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P|  0.0029292|  0.0003775  | 7.759| 6.77e-12 |***
Q | 0.0373053 | 0.0025151 | 14.832 | < 2e-16 |***
c1 |0.0185380  |0.0032489|   5.706 |1.14e-07| ***
```{r}
# one-way effect
# cases add on news

# from 2020-03-10 to 2020-04-10
# start=list(M=4, P=0.001, Q=0.1)
# m_c <- cases_coef要記得調整
# Cases <- c(16, 21, 0, 72, 50, 47, 80, 75, 116, 113, 110, 280, 419, 192, 362, 320, 446, 333, 497, 344, 377, 198, 303, 254, 214, 220, 137, 110, 98, 115, 98, 107)

# from 2020-03-13 to 2020-04-24
Cases <- c(72, 50, 47, 80, 75, 116, 113, 110, 280, 419, 192, 362, 320, 446, 333, 497, 344, 377, 198, 303, 254, 214, 220, 137, 110, 98, 115, 98, 107, 88, 12, 36, 64, 25, 22, 60, 25, 0, 0, 0, 0, 114, 16)

# from 2020-01-11 to 2020-04-24
News <- c(12, 11, 27, 21, 30, 8, 11, 3, 16, 23, 39, 40, 32, 44, 14, 32, 44, 69, 36, 47, 31, 33, 24, 43, 50, 36, 38, 27, 15, 18, 30, 44, 41, 52, 33, 30, 39, 48, 49, 74, 76, 58, 31, 42, 63, 63, 84, 60, 51, 35, 36, 70, 89, 80, 73, 65, 31, 48, 71, 75, 72, 65, 78, 39, 51, 70, 98, 101, 95, 64, 41, 42, 83, 91, 91, 89, 61, 71, 57, 74, 77, 81, 75, 86, 73, 49, 81, 80, 76, 65, 59, 62, 51, 59, 69, 82, 60, 84, 59, 61, 87, 72, 79, 80, 57)

Cases <- Cases / sum(Cases)
T_day <- 1:length(Cases)
c_nls <- nls(
  Cases ~ 1 * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day)) / (1 + (Q / P) * exp(-(P + Q) * T_day)) ^ 2,
  start=list(P=0.001, Q=0.1)
  #start=list(M=10000, P=0.003, Q=0.38)
)
summary(c_nls)

cases_coef <- coef(c_nls)
p_c <- cases_coef[1]
q_c <- cases_coef[2]
m_c <- 1

News <- News / sum(News)
T_day_news <- 1:length(News)
zeroes = length(T_day_news) - length(T_day)
T_day <- c(rep(0, zeroes), T_day)
# estimates of news come in to the formula to perform co-diffusion
# c1 is coefficient of cases
# F = (1 - exp(-(P + Q) * t)) / (1 + (Q / P) * exp(-(P + Q) * t))
# News ~ M * f1 = M * (原本bass那串 + c1 * F2(t) * (1 - F1(t)))
n_nls <- nls(
  News ~ 1 * ((((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2 + c1 * (1 - exp(-(p_c + q_c) * T_day)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * T_day)) * (1 - (1 - exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)))),
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.03, Q=0.038, c1=0.1)
)
summary(n_nls)

news_coef <- coef(n_nls)
p_n <- news_coef[1]
q_n <- news_coef[2]
c1_n <- news_coef[3]
m_n <- 1




# w/o co-diffusion
n_wo_cd_nls <- nls(
  News ~ 1 * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2,
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.003, Q=0.038)
  #start=list(M=3, P=0.03, Q=0.0038, c1=0.1),
)
summary(n_wo_cd_nls)
news_wo_cd_coef <- coef(n_wo_cd_nls)
p_n_wo_cd <- news_wo_cd_coef[1]
q_n_wo_cd <- news_wo_cd_coef[2]
m_n_wo_cd <- 1




# simulation
Tdelt <- (1:(length(Cases) * 10)) / 10
ngete <- exp(-(p_c + q_c) * Tdelt)
cpdf <- m_c * ((p_c + q_c) ^ 2 / p_c) * ngete / (1 + (q_c / p_c) * ngete) ^ 2

Tdelt <- (1:(length(News) * 10)) / 10
Tdelt_cases <-ifelse(Tdelt - zeroes < 0, 0, Tdelt - zeroes)

ngete_wo_cd <- exp(-(p_n_wo_cd + q_n_wo_cd) * Tdelt)
n_wo_cd_pdf <- m_n_wo_cd * ((p_n_wo_cd + q_n_wo_cd) ^ 2 / p_n_wo_cd) * ngete_wo_cd / (1 + (q_n_wo_cd / p_n_wo_cd) * ngete_wo_cd) ^ 2

ngete <- exp(-(p_n + q_n) * Tdelt)
npdf <- m_n * (((p_n + q_n) ^ 2 / p_n) * ngete / (1 + (q_n / p_n) * ngete) ^ 2 + c1_n * (1 - exp(-(p_c + q_c) * Tdelt_cases)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * Tdelt_cases)) * (1 - (1 - exp(-(p_n + q_n) * Tdelt)) / (1 + (q_n / p_n) * exp(-(p_n + q_n) * Tdelt))))

cpdf <- c(rep(0, zeroes * 10), cpdf)
Cases <- c(rep(0, zeroes), Cases)

# cases is higher so plot cases first
plot(cpdf ~ Tdelt, col=5, type='l', xlab = "Day from 1/11", ylab = "Quantity", main = "Co-diffusion of cases and news in AU")
points(T_day_news, Cases, col=5, pch=6)
points(News ~ T_day_news, col='blue', pch=4)
lines(Tdelt, npdf, col='blue')
lines(Tdelt, n_wo_cd_pdf, col='red', lty=2)
legend("topleft",
       pch = c(6, 4),
       col = c(5, 'blue'),
       legend = c("Cases", "News")
       )
```


# CA one way

## Cases 2020/03/15 - 2020/04/24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
M| 1.5098915  |0.2351892|   6.420 |1.51e-07| ***
P |0.0034999 | 0.0008755 |  3.998 |0.000284 |***
Q |0.0945436|  0.0180356  | 5.242| 6.22e-06 |***

##  News 2020/01/11 - 2020-04-24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P|  0.0018914  |0.0002888|   6.550 |2.38e-09| ***
Q | 0.0428883 | 0.0025510 | 16.812 | < 2e-16 |***
c1 |0.0604855|  0.0103192  | 5.861| 5.68e-08 |***
```{r}
# one-way effect
# cases add on news

# from 2020-03-10 to 2020-04-13
#Cases <- c(3, 29, 9, 76, 3, 54, 165, 63, 179, 143, 143, 335, 192, 618, 702, 461, 791, 640, 894, 704, 1118, 1129, 1033, 1724, 1153, 541, 2778, 807, 1309, 1269, 1513, 1405, 1257, 983, 1381)

#from 2020-03-15 to 2020-04-24
Cases <- c(54, 165, 63, 179, 143, 143, 335, 192, 618, 702, 461, 791, 640, 894, 704, 1118, 1129, 1033, 1724, 1153, 541, 2778, 807, 1309, 1269, 1513, 1405, 1257, 983, 1381, 1355, 1174, 2600, 2005, 1542, 1277, 2025, 1744, 2248, 1636, 770)

# from 2020-01-22 to 2020-04-13
#News <- c(39, 55, 52, 20, 23, 33, 33, 31, 35, 25, 19, 16, 16, 40, 19, 29, 18, 12, 12, 25, 22, 17, 43, 29, 23, 17, 35, 54, 43, 28, 24, 28, 17, 50, 43, 41, 32, 61, 29, 40, 65, 77, 49, 87, 73, 50, 29, 66, 49, 51, 49, 45, 34, 50, 76, 50, 67, 75, 88, 32, 56, 92, 98, 76, 64, 69, 44, 40, 100, 76, 45, 70, 41, 26, 28, 25, 37, 50, 4, 26, 12, 1)

# from 2020-01-11 to 2020-04-24
News <- c(11, 9, 19, 21, 11, 17, 28, 8, 8, 35, 30, 37, 41, 42, 21, 18, 21, 41, 28, 26, 22, 10, 16, 16, 29, 19, 18, 20, 9, 14, 17, 15, 17, 14, 10, 5, 13, 44, 57, 47, 41, 44, 31, 26, 55, 52, 57, 52, 70, 44, 39, 65, 66, 65, 75, 78, 43, 32, 106, 78, 73, 65, 61, 37, 58, 72, 69, 60, 75, 68, 45, 50, 68, 79, 70, 72, 86, 48, 48, 85, 78, 76, 102, 78, 53, 49, 89, 84, 93, 56, 45, 38, 64, 88, 101, 83, 85, 84, 69, 61, 89, 87, 92, 96, 58)

Cases <- Cases / sum(Cases)
T_day <- 1:length(Cases)
c_nls <- nls(
  Cases ~ M * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day)) / (1 + (Q / P) * exp(-(P + Q) * T_day)) ^ 2,
  start=list(M=4, P=0.001, Q=0.1)
  #start=list(M=10000, P=0.003, Q=0.38)
)
summary(c_nls)

cases_coef <- coef(c_nls)
m_c <- cases_coef[1]
p_c <- cases_coef[2]
q_c <- cases_coef[3]

News <- News / sum(News)
T_day_news <- 1:length(News)
zeroes = length(T_day_news) - length(T_day)
T_day <- c(rep(0, zeroes), T_day)
# estimates of news come in to the formula to perform co-diffusion
# c1 is coefficient of cases
# F = (1 - exp(-(P + Q) * t)) / (1 + (Q / P) * exp(-(P + Q) * t))
# News ~ M * f1 = M * (原本bass那串 + c1 * F2(t) * (1 - F1(t)))
n_nls <- nls(
  News ~ 1 * ((((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2 + c1 * (1 - exp(-(p_c + q_c) * T_day)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * T_day)) * (1 - (1 - exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)))),
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.03, Q=0.038, c1=0.1)
)
summary(n_nls)

news_coef <- coef(n_nls)
p_n <- news_coef[1]
q_n <- news_coef[2]
c1_n <- news_coef[3]
m_n <- 1


# w/o co-diffusion
n_wo_cd_nls <- nls(
  News ~ 1 * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2,
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.003, Q=0.038)
  #start=list(M=3, P=0.03, Q=0.0038, c1=0.1),
)
summary(n_wo_cd_nls)
news_wo_cd_coef <- coef(n_wo_cd_nls)
p_n_wo_cd <- news_wo_cd_coef[1]
q_n_wo_cd <- news_wo_cd_coef[2]
m_n_wo_cd <- 1


# simulation
Tdelt <- (1:(length(Cases) * 10)) / 10
ngete <- exp(-(p_c + q_c) * Tdelt)
cpdf <- m_c * ((p_c + q_c) ^ 2 / p_c) * ngete / (1 + (q_c / p_c) * ngete) ^ 2

Tdelt <- (1:(length(News) * 10)) / 10
Tdelt_cases <-ifelse(Tdelt - zeroes < 0, 0, Tdelt - zeroes)

ngete <- exp(-(p_n + q_n) * Tdelt)
npdf <- m_n * (((p_n + q_n) ^ 2 / p_n) * ngete / (1 + (q_n / p_n) * ngete) ^ 2 + c1_n * (1 - exp(-(p_c + q_c) * Tdelt_cases)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * Tdelt_cases)) * (1 - (1 - exp(-(p_n + q_n) * Tdelt)) / (1 + (q_n / p_n) * exp(-(p_n + q_n) * Tdelt))))


ngete_wo_cd <- exp(-(p_n_wo_cd + q_n_wo_cd) * Tdelt)
n_wo_cd_pdf <- m_n_wo_cd * ((p_n_wo_cd + q_n_wo_cd) ^ 2 / p_n_wo_cd) * ngete_wo_cd / (1 + (q_n_wo_cd / p_n_wo_cd) * ngete_wo_cd) ^ 2

cpdf <- c(rep(0, zeroes * 10), cpdf)
Cases <- c(rep(0, zeroes), Cases)

# cases is higher so plot cases first
plot(cpdf ~ Tdelt, col=5, type='l', xlab = "Day from 1/11", ylab = "Quantity", main = "Co-diffusion of cases and news in CA")
points(T_day_news, Cases, col=5, pch=6)
points(News ~ T_day_news, col='blue', pch=4)
lines(Tdelt, npdf, col='blue')
lines(Tdelt, n_wo_cd_pdf, col='red', lty=2)
legend("topleft",
       pch = c(6, 4),
       col = c(5, 'blue'),
       legend = c("Cases", "News")
       )
```


# TW one way

## Cases 2020/03/10 - 2020/04/24

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P| 0.008277 |  0.002052|   4.034 |0.000215| ***
Q |0.199345|   0.020898 |  9.539| 2.81e-12 |***

##  News 2020/01/11 - 2020-04-24
Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P|  0.0075716  |0.0008421|   8.991 |8.27e-14| ***
Q | 0.0485094 | 0.0041096 | 11.804 | < 2e-16 |***
c1 |0.0139132|  0.0067984  | 2.047|   0.0439 |*
```{r}
# one-way effect
# cases add on news

# from 2020-03-10 to 2020-04-24
Cases <- c(2, 1, 1, 1, 3, 6, 8, 10, 23, 8, 27, 18, 16, 26, 20, 20, 17, 15, 16, 15, 8, 16, 7, 10, 9, 7, 8, 10, 3, 3, 1, 2, 3, 3, 5, 0, 2, 0, 0, 3, 22, 2, 3, 1, 1, 1)

# from 2020-02-15 to 2020-04-24
News <- c(134, 197, 204, 135, 139, 157, 146, 128, 140, 139, 141, 146, 154, 129, 177, 145, 148, 226, 260, 180, 161, 82, 104, 132, 140, 149, 100, 120, 94, 114, 133, 123, 124, 130, 132, 109, 129, 112, 136, 161, 111, 103, 100, 179, 160, 128, 83, 85, 72, 71, 67, 52, 84, 88, 75, 83, 57, 43, 76, 75, 73, 77, 80, 59, 99, 73, 94, 80, 57, 92)

# from 2020-02-01 to 2020-04-24
News <- c(45, 34, 63, 52, 53, 37, 45, 34, 53, 61, 38, 136, 166, 202, 134, 197, 204, 135, 139, 157, 146, 128, 140, 139, 141, 146, 154, 129, 177, 145, 148, 226, 260, 180, 161, 82, 104, 132, 140, 149, 100, 120, 94, 114, 133, 123, 124, 130, 132, 109, 129, 112, 136, 161, 111, 103, 100, 179, 160, 128, 83, 85, 72, 71, 67, 52, 84, 88, 75, 83, 57, 43, 76, 75, 73, 77, 80, 59, 99, 73, 94, 80, 57, 92)

plot(Cases)
plot(News)

Cases <- Cases / sum(Cases)
T_day <- 1:length(Cases)
c_nls <- nls(
  Cases ~ 1 * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day)) / (1 + (Q / P) * exp(-(P + Q) * T_day)) ^ 2,
  start=list(P=0.01, Q=0.1)
  #start=list(M=10000, P=0.003, Q=0.38)
)
summary(c_nls)

cases_coef <- coef(c_nls)
#m_c <- cases_coef[1]
m_c <- 1
p_c <- cases_coef[1]
q_c <- cases_coef[2]

News <- News / sum(News)
T_day_news <- 1:length(News)
zeroes = length(T_day_news) - length(T_day)
T_day <- c(rep(0, zeroes), T_day)
T_day
# estimates of news come in to the formula to perform co-diffusion
# c1 is coefficient of cases
# F = (1 - exp(-(P + Q) * t)) / (1 + (Q / P) * exp(-(P + Q) * t))
# News ~ M * f1 = M * (原本bass那串 + c1 * F2(t) * (1 - F1(t)))
n_nls <- nls(
  News ~ 1 * ((((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2 + c1 * (1 - exp(-(p_c + q_c) * T_day)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * T_day)) * (1 - (1 - exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)))),
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.03, Q=0.038, c1=0.1)
)
summary(n_nls)

news_coef <- coef(n_nls)
p_n <- news_coef[1]
q_n <- news_coef[2]
c1_n <- news_coef[3]
m_n <- 1

# simulation
Tdelt <- (1:(length(Cases) * 10)) / 10
ngete <- exp(-(p_c + q_c) * Tdelt)
cpdf <- m_c * ((p_c + q_c) ^ 2 / p_c) * ngete / (1 + (q_c / p_c) * ngete) ^ 2

Tdelt <- (1:(length(News) * 10)) / 10
Tdelt_cases <-ifelse(Tdelt - zeroes < 0, 0, Tdelt - zeroes)

ngete <- exp(-(p_n + q_n) * Tdelt)
npdf <- m_n * (((p_n + q_n) ^ 2 / p_n) * ngete / (1 + (q_n / p_n) * ngete) ^ 2 + c1_n * (1 - exp(-(p_c + q_c) * Tdelt_cases)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * Tdelt_cases)) * (1 - (1 - exp(-(p_n + q_n) * Tdelt)) / (1 + (q_n / p_n) * exp(-(p_n + q_n) * Tdelt))))

cpdf <- c(rep(0, zeroes * 10), cpdf)
Cases <- c(rep(0, zeroes), Cases)

# cases is higher so plot cases first
plot(cpdf ~ Tdelt, col=5, type='l', xlab = "Day from 2/1", ylab = "Quantity", main = "Co-diffusion of cases and news in TW")
points(T_day_news, Cases, col=5, pch=6)
points(News ~ T_day_news, col='blue', pch=4)
lines(Tdelt, npdf, col='blue')
legend("topleft",
       pch = c(6, 4),
       col = c(5, 'blue'),
       legend = c("Cases", "News")
       )
```


# CN one way

## Cases 2020/01/23 - 2020-03-09

Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P |0.004270 |  0.002451|   1.742 |  0.0884| .   (因那一天的極端值) 
Q |0.203826|   0.038377 |  5.311| 3.24e-06 |***

##  News 2020/01/05 - 2020-03-09
Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P|   0.0012169  |0.0001898|   6.412 |2.21e-08| ***
Q |  0.1005110 | 0.0058224 | 17.263 | < 2e-16 |***
c1 |-0.0347552|  0.0038236  |-9.090| 5.22e-13 |***

## Cases 拔掉極值(15136)則
Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P| 0.007666 |  0.002089|   3.669 |0.000654| ***
Q |0.198893|   0.022243 |  8.942| 1.87e-11 |***

##  News
Param.  |  Estimate  | Std.        | Error    | t value    | Pr(>\|t\|)
------- | ---------- | ----------- | -------- | ---------- | --------
P|   0.0012978  |0.0002043|   6.351 |2.81e-08| ***
Q |  0.1007428 | 0.0060422 | 16.673 | < 2e-16 |***
c1 |-0.0329952|  0.0037591  |-8.778| 1.79e-12 |***
```{r}
# one-way effect
# cases add on news

# from 2020-01-23 to 2020-03-09
Cases <- c(95, 277, 486, 669, 802, 2632, 578, 2054, 1661, 2089, 4739, 3086, 3991, 3733, 3147, 3523, 2704, 3015, 2525, 2032, 373, 15136, 6463, 2055, 2100, 1921, 1777, 408, 458, 473, 1451, 21, 219, 513, 412, 434, 328, 428, 576, 204, 125, 125, 151, 153, 80, 53, 37)

Cases <- c(95, 277, 486, 669, 802, 2632, 578, 2054, 1661, 2089, 4739, 3086, 3991, 3733, 3147, 3523, 2704, 3015, 2525, 2032, 373, 6463, 2055, 2100, 1921, 1777, 408, 458, 473, 1451, 21, 219, 513, 412, 434, 328, 428, 576, 204, 125, 125, 151, 153, 80, 53, 37)

# from 2020-01-05 to 2020-03-09
News <- c(4, 6, 1, 1, 16, 1, 19, 2, 4, 2, 4, 3, 13, 8, 16, 62, 76, 103, 108, 84, 94, 108, 94, 149, 135, 133, 132, 116, 141, 164, 163, 156, 152, 125, 148, 148, 151, 143, 131, 167, 146, 121, 118, 132, 115, 113, 123, 182, 120, 111, 86, 135, 124, 126, 120, 94, 155, 118, 107, 115, 132, 117, 80, 88, 82)

Cases <- Cases / sum(Cases)
T_day <- 1:length(Cases)
c_nls <- nls(
  Cases ~ 1 * (((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day)) / (1 + (Q / P) * exp(-(P + Q) * T_day)) ^ 2,
  start=list(P=0.01, Q=0.1)
  #start=list(M=10000, P=0.003, Q=0.38)
)
summary(c_nls)

cases_coef <- coef(c_nls)
#m_c <- cases_coef[1]
m_c <- 1
p_c <- cases_coef[1]
q_c <- cases_coef[2]

News <- News / sum(News)
T_day_news <- 1:length(News)
zeroes = length(T_day_news) - length(T_day)
T_day <- c(rep(0, zeroes), T_day)
# estimates of news come in to the formula to perform co-diffusion
# c1 is coefficient of cases
# F = (1 - exp(-(P + Q) * t)) / (1 + (Q / P) * exp(-(P + Q) * t))
# News ~ M * f1 = M * (原本bass那串 + c1 * F2(t) * (1 - F1(t)))
n_nls <- nls(
  News ~ 1.9 * ((((P + Q) ^ 2 / P) * exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)) ^ 2 + c1 * (1 - exp(-(p_c + q_c) * T_day)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * T_day)) * (1 - (1 - exp(-(P + Q) * T_day_news)) / (1 + (Q / P) * exp(-(P + Q) * T_day_news)))),
  #start=list(M=8000, P=0.03, Q=0.038, c1=0.03)
  start=list(P=0.001, Q=0.1, c1=-0.1)
)
summary(n_nls)

news_coef <- coef(n_nls)
#m_n <- news_coef[1]
m_n <- 1.9
p_n <- news_coef[1]
q_n <- news_coef[2]
c1_n <- news_coef[3]

# simulation
Tdelt <- (1:(length(Cases) * 10)) / 10
ngete <- exp(-(p_c + q_c) * Tdelt)
cpdf <- m_c * ((p_c + q_c) ^ 2 / p_c) * ngete / (1 + (q_c / p_c) * ngete) ^ 2

Tdelt <- (1:(length(News) * 10)) / 10
Tdelt_cases <-ifelse(Tdelt - zeroes < 0, 0, Tdelt - zeroes)

ngete <- exp(-(p_n + q_n) * Tdelt)
npdf <- m_n * (((p_n + q_n) ^ 2 / p_n) * ngete / (1 + (q_n / p_n) * ngete) ^ 2 + c1_n * (1 - exp(-(p_c + q_c) * Tdelt_cases)) / (1 + (q_c / p_c) * exp(-(p_c + q_c) * Tdelt_cases)) * (1 - (1 - exp(-(p_n + q_n) * Tdelt)) / (1 + (q_n / p_n) * exp(-(p_n + q_n) * Tdelt))))

cpdf <- c(rep(0, zeroes * 10), cpdf)
Cases <- c(rep(0, zeroes), Cases)

# cases is higher so plot cases first
plot(cpdf ~ Tdelt, col=5, type='l', xlab = "Day from 1/5", ylab = "Quantity", main = "Co-diffusion of cases and news in CN")
points(T_day_news, Cases, col=5, pch=6)
points(News ~ T_day_news, col='blue', pch=4)
lines(Tdelt, npdf, col='blue')
legend("topleft",
       pch = c(6, 4),
       col = c(5, 'blue'),
       legend = c("Cases", "News")
       )
```


Cases by Country
# US one way
## Cases 2020/03/07 - 2020-04-24
M 1.3159331  0.0640758  20.537  < 2e-16 ***
P 0.0016618  0.0002744   6.057 2.38e-07 ***
Q 0.1095144  0.0072015  15.207  < 2e-16 ***
# UK one way
## Cases 2020/03/12 - 2020/04/24
M 1.3123825  0.0830045   15.81  < 2e-16 ***
P 0.0024500  0.0004571    5.36 3.74e-06 ***
Q 0.1149791  0.0100024   11.49 2.99e-14 ***
# AU one way
## Cases 2020/03/13 - 2020/04/24
P 0.006141   0.001029    5.97 4.78e-07 ***
Q 0.227823   0.013657   16.68  < 2e-16 ***
# CA one way
## Cases 2020/03/15 - 2020/04/24
M 1.5098915  0.2351892   6.420 1.51e-07 ***
P 0.0034999  0.0008755   3.998 0.000284 ***
Q 0.0945436  0.0180356   5.242 6.22e-06 ***
# TW one way
## Cases 2020/03/10 - 2020/04/24
P 0.008277   0.002052   4.034 0.000215 ***
Q 0.199345   0.020898   9.539 2.81e-12 ***
# CN one way
## 拔掉極值(15136)則
## Cases
P 0.007666   0.002089   3.669 0.000654 ***
Q 0.198893   0.022243   8.942 1.87e-11 ***
